### 2023-03-29 main/chapter_experiment.tex
add muon resolution

Our search paper~\cite{atlas2022searches} contains concise and standard
descriptions of the \atlas\ detector and its relevant components.
Through its evolution in many past \atlas\ publications, these descriptions
have become so highly refined that attempts to improve them myself would
probably be in vain.
Instead, this section quotes our published text with explanatory commentary.
\begin{quote}
``%
The ATLAS detector~\cite{atlas2008experiment} is a multipurpose particle
detector with a forward--backward symmetric cylindrical geometry and a near
$4\pi$ coverage in solid angle.%
\footnote{%
``ATLAS uses a right-handed coordinate system with its origin at the nominal
interaction point (IP) in the centre of the detector and the $z$-axis along the
beam pipe.
The $x$-axis points from the IP to the centre of the LHC ring, and the $y$-axis
points upwards.
Cylindrical coordinates $(r,\phi)$ are used in the transverse plane, $\phi$
being the azimuthal angle around the $z$-axis.
The pseudorapidity is defined in terms of the polar angle $\theta$ as
$\eta = -\ln \tan(\theta/2)$.
Angular distance is measured in units of
$\Delta R \equiv \sqrt{(\Delta\eta)^{2} + (\Delta\phi)^{2}}$.%
''\footnotemark~\cite{atlas2022searches}%
}
It consists of an inner tracking detector surrounded by a thin superconducting
solenoid providing a $2\,\mathrm{T}$ axial magnetic field, electromagnetic and
hadronic calorimeters, and a muon spectrometer.%
''~\cite{atlas2022searches}
\end{quote}
To illustrate this summary, Figure~\ref{fig:atlas_cutaway} shows a vertical slice
of \atlas.
Each subsystem is described in more detail in a subsection below:
the inner tracking detector in Section~\ref{sec:atlas_inner},
the electromagnetic and hadronic calorimeters in
Section~\ref{sec:atlas_calo},
and
the muon spectrometer in Section~\ref{sec:atlas_muon}.
The final connection to data analysed in this thesis is made through the
trigger system, which is described in Section~\ref{sec:atlas_trigger},
and details of the data themselves are given in
Section~\ref{sec:atlas_data}.

@@

>>>>

Our search paper~\cite{atlas2022searches} contains concise and standard
descriptions of the \atlas\ detector and its relevant components.
Through its evolution in many past \atlas\ publications, these descriptions
have become so highly refined that attempts to improve them myself would
probably be in vain.
Instead, this section quotes our published text with explanatory commentary.
\begin{quote}
``%
The ATLAS detector~\cite{atlas2008experiment} is a multipurpose particle
detector with a forward--backward symmetric cylindrical geometry and a near
$4\pi$ coverage in solid angle.%
\footnote{%
``ATLAS uses a right-handed coordinate system with its origin at the nominal
interaction point (IP) in the centre of the detector and the $z$-axis along the
beam pipe.
The $x$-axis points from the IP to the centre of the LHC ring, and the $y$-axis
points upwards.
Cylindrical coordinates $(r,\phi)$ are used in the transverse plane, $\phi$
being the azimuthal angle around the $z$-axis.
The pseudorapidity is defined in terms of the polar angle $\theta$ as
$\eta = -\ln \tan(\theta/2)$.
Angular distance is measured in units of
$\Delta R \equiv \sqrt{(\Delta\eta)^{2} + (\Delta\phi)^{2}}$.%
''\footnotemark~\cite{atlas2022searches}%
}
It consists of an inner tracking detector surrounded by a thin superconducting
solenoid providing a $2\,\mathrm{T}$ axial magnetic field, electromagnetic and
hadronic calorimeters, and a muon spectrometer.%
''~\cite{atlas2022searches}
\end{quote}
To illustrate this summary, Figure~\ref{fig:atlas_cutaway} shows a vertical slice
of \atlas.
Each subsystem is described in more detail in a subsection below:
the inner tracking detector in Section~\ref{sec:atlas_inner},
the electromagnetic and hadronic calorimeters in
Section~\ref{sec:atlas_calo},
and
the muon spectrometer in Section~\ref{sec:atlas_muon}.
These detectors' resolutions to relevant physical objects is described in
Section~\label{sec:atlas_object_resolutions}.
The final connection to data analysed in this thesis is made through the
trigger system, which is described in Section~\ref{sec:atlas_trigger},
and details of the data themselves are given in
Section~\ref{sec:atlas_data}.

@@

\section{Object resolutions}
\label{sec:atlas_object_resolutions}
Ultimately, the majority usage of most of \atlas's data happens through their
reconstructions into interpretable objects, such as muons, electrons, jets,
photons, or taus.
From one perspective, these reconstructions are themselves exact data, as they
are nothing less than functions of observed data.
However, reconstructed objects do not exactly coincide with some proposed
underlying truth --- reconstructions more closely resemble that truth perturbed
by some noise.
\atlas's experimental resolution determines the scale of that noise.

Since the $\twoljets$ analysis is most concerned with muons, electrons and
jets.
\TODO{and missing transverse momentum},
this section reviews \atlas's experimental resolution for these objects.

\paragraph{Muons.}
Since hard muons are not stopped inside \atlas, their reconstruction derives
from the curved tracks they leave in the inner detector and muon system as they
traverse \atlas's strong magnetic fields.
High tracking fidelity allows us to reliably reconstruct muons across most of
their expected momentum spectrum, with $\sigma(\pt) / \pt \lesssim 10\%$ up to
$\pt \approx 1\,\eV[T]$.
But resolution must degrade as these tracks' curvatures reduce at very high
energies, and Figure~\ref{fig:atlas_cutaway} illustrates this degradation.
The relative momentum resolution is approximately Gaussian in
$\sigma(\pt) / \pt$ for muons across this momentum range
(and therefore non-Gaussian in $\pt$ itself)~\cite{atlas1999design1}.

At a reference transverse momentum of $\pt = 100\,\eV[G]$, \atlas's typical
relative muon momentum resolution is at the $\sigma(\pt) / \pt \approx 2\%$
level.
However, non-uniformities in the detector geometry cause this to spike up to
$\approx 10\%$ in local areas of the $\eta\textrm{--}\phi$ angular space;
these degraded local areas include regions containing cryostat hardware or
the detector's supporting feet~\cite{atlas1999design1, CERN-LHCC-97-022}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.8\textwidth]{figures/atlas_muon_resolution.pdf}
\caption[
Relative muon momentum resolution in \atlas\ as a function of $\pt$
]{%
Relative muon momentum resolution in \atlas\ as a function of $\pt$, for
muons selected within a pseudorapidity window of $|\eta| < 1.5$ and averaged
over that window.
The dots mark resolution values extracted from simulations, and the line
represents a semi-empirical description of the relative
resolution~\cite{CERN-LHCC-97-022}.
This figure is reproduced from~\cite{atlas1999design1}.
}
\label{fig:atlas_cutaway}
\end{figure}

\paragraph{Electrons.}

\paragraph{Jets.}

\paragraph{Missing transverse momentum.}
\TODO{}
